Summary of 2022 experiments

### 2024-05-17 code/early_expts_summary.Rmd
poking at models

outcome ~ log(words_first_10)*game_type*words_now ?

@@

early_word_mod <- brm(payoff ~ log_early_words * is_BoS + is_chat*is_BoS+ repNum + 
                  (is_BoS | gameId) + 
                  (is_BoS | playerId),
  data = for_early_word_mod,
  prior = perf_priors,
  control = list(adapt_delta = .95)
)

>>>>

```{r}

ggplot(for_log_words, aes(x=log_words, y=payoff, color=repNum))+geom_jitter(alpha=.5)+geom_smooth(method="lm")+facet_wrap(is_BoS~cond)
```

TODO think more about!!
outcome ~ log(words_first_10)*game_type*words_now ?

@@

early_word_mod <- brm(payoff ~ log_early_words * is_BoS* is_chat+ repNum + 
                  (is_BoS | gameId) + 
                  (is_BoS | playerId),
  data = for_early_word_mod,
  prior = perf_priors,
  control = list(adapt_delta = .95)
)
